\section{Introduction To Project} 
With the launch and increase in sales of web applications over the last few years, people are using
computers to get their work done, which makes their lives easier.Web application comprise various different categories such as Entertainment, Sports, Lifestyle, Education,
Games,Food and Drink, Health and Fitness, Finance, etc. The application falls under Sports
category and helps the students to access all the news related to sports department of Guru
Nanak Dev Engineering College , Ludhiana .
The applications interface is designed using custom art elements, the functionality is imple-
mented using technologies such as javascript, css, html , and the phase of testing the product was accomplished successfully. The application can very well manage,store and share different news related to sports
among different users.Students who are Sports enthusiastic can get full information of sports
department.Admin panel can upload news and student panel can view those news in the systems. Description of sports depatment such as commitee menbers , facilities , scholarships ,
achievements and other optional attributes ( Adding latest news to the in applications). All
these topics have been explained in detail in their respective chapters.

\section{Project Category(Internet based, Application or System Development)}
This application is web based application based on internet using real time NoSql database(Firebase Database).

\section{Objectives}

\begin{itemize}
	\item  To study the enhancement of retinal image.

	\item To process an retinal image so that the output image is more enhanced than the original image..
	
	\item To perform the objective evaluation of the result and tell about the best image.


\end{itemize}

\section{Problem Formulation}
Through our project, medical team or doctors will be able to give a better assessment of the images for the proper treatment of the various eye related problems and can help in find out about various eye realted diseases  .   

\section{Proposed System Modules}

\begin{itemize}
	\item User will be able to select retinal image for various image operations.

	\item Time will be saved as doctors will find the disease much faster through the image  .
	
	\item Medical team will give assesment about the best possible image.   
	
	
	


\end{itemize}

 
\section{Unique Features of the System}
\begin{itemize}

\item Time will be saved as doctors will find the disease much faster through the image  .
\item To process an retinal image so that the output image is more enhanced than the original image.

\item User will be able to select retinal image for various image operations..

\item Medical team will give assesment about the best possible image.

\end{itemize}


